### 2019-07-30 thesis.tex
another day writing the thesis...

Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, and scale lengths\footnote{For a relatively brief, but
  comprehensive, description of the scales and characteristics of cosmic plasmas,
  see Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the outer layers of
Earth's atmosphere, passing through the solar wind in the interplanetary space,
to the stellar interiors and atmospheres, accretion disks, and molecular clouds
it is estimated that something around $99 \sim 99.9\%$ of the observable matter
in the universe is in the plasma state\cite{may}. Most of these plasmas are quite
far from our measurement instruments, being accessible only through analysis of
the electromagnetic spectrum emitted from their remote location.

>>>>

Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, and scale lengths\footnote{For a relatively brief, but
  comprehensive, description of the scales and characteristics of cosmic plasmas,
  see Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the outer layers of
Earth's atmosphere, passing through the solar wind in the interplanetary space,
to the stellar interiors and atmospheres, accretion disks, and molecular clouds
it is estimated that something around $99 \sim 99.9\%$ of the observable matter
in the universe is in the plasma state\cite{may}. The absolute majority of space
plasmas are unreachable to in situ observation, being accessible only through
analysis of the electromagnetic spectrum emitted from their remote location.
